; AlifeBalance inventory policy. Per-category {min, max} ceilings for the inventory
; balance scanner (ab_loot_balance.script). Uniform single block; no per-rank tiers.
; DLTX-overridable. Shape parsed by xinventory.load_policy.
;
; Backstop semantics: scanner releases items above max in each category. Higher ceilings
; than the AlifePlus trade policy (ap_trade_policy.ltx) because trade does the primary
; economic enforcement (sells surplus, restocks combat load); the scanner catches what
; trade misses -- long-lived NPCs (story NPCs, companions, gulag survivors) that never
; visit traders.
;
; Ammo categories count in ROUNDS; other categories count in items. Sentinel categories
; (untouchable, equipped, other) are pre-filtered by xinventory and never reach this
; policy. Categories with max=0 release on sight (mismatched ammo, non-equipped weapons,
; outfits / helmets / artefacts / crafting / devices that NPCs do not actively use).

[ab_inventory_policy]
ammo_slot_3_t1    = 0, 200    ; rifle basic ammo (rounds; ~7 mags)
ammo_slot_3_t2    = 0, 200    ; rifle AP ammo (rounds)
ammo_slot_2_t1    = 0, 64     ; pistol basic ammo (rounds; ~4 mags)
ammo_slot_2_t2    = 0, 64     ; pistol AP ammo (rounds)
ammo_not_equipped = 0, 0      ; ammo not matching any equipped weapon
grenade           = 0, 3
grenade_ammo      = 0, 10
medkit            = 0, 20
bandage           = 0, 20
antirad           = 0, 10
stim              = 0, 10
pill              = 0, 10
food              = 0, 10
drink             = 0, 5
weapon            = 0, 0      ; non-equipped ruck weapons
outfit            = 0, 0
helmet            = 0, 0
artefact          = 0, 0
device            = 0, 0
money             = 0, 0
crafting          = 0, 0
other             = 0, 0
